Lab 2 Final Report: COVID-19 Case Rate vs Population Demographics and Mask Policy

### 2020-12-04 Jackson_Liu_Temlock_Zhang_Lab2_Draft_Report.Rmd
Update Jackson_Liu_Temlock_Zhang_Lab2_Draft_Report.Rmd
udpate model 3

### @Frank, this was my previous analysis of the POPULATION DENSITY variable, feel free to use any of this

@@

Next, the regression model for model 3 is based on the existing work from model 2. Two additional variables will be introduced as maximalist approach. The first variable is the "mask_public_bool" (whether the state enforced public mask mandate or not) that represents the policy effects. The second variable introduced is "population_density" (the value is logged as discussed earlier) which is considered an important factor considering nature of spread in disease.

@@

The population density variable however is not significant in the regression even it is considered as one of the major factors to the spread of disease. So according to the regression, we fail to reject the null hypothesis that population density have an direct impact to the COVID-19 case rate. There could be multiple factors causing the population density to be insignificant. For example, the population density is calculated by population divided by total square miles. As a result the numbers can be diluted for states that have major cities with high population density, but very little urbanization in the majority part of the state suburb area. In addition, as stated earlier in the research, Washington, D.C. is considered as a state however the demography structure and geographical related characteristics are different from other states. And due to a sample sample we have, individual variables that exhibit unique characteristics could lead to certain degree of bias.

@@

CLM assumptions check for Model 3:
```{r}
#Zero Conditional Mean
plot(model3, which=1)

#Normality of errors
plot(model3, which=2)

#Homoskedasticity
plot(model3, which=3)

#Cook distance
plot(model3, which=5)

#Collinearity
vif(model3)
```

>>>>

@@

Next, the regression model for model 3 is based on the existing work from model 2. Two additional variables discussed in Model 3 will be introduced as maximalist approach. The first variable is the "mask_public_bool" (whether the state enforced public mask mandate or not) that represents the policy effects. The second variable introduced is "population_density" (the value is logged as discussed earlier) which is considered an important factor considering nature of spread in disease.

@@

The population density variable however is not significant in the regression even it is considered as one of the major factors to the spread of disease. So according to the regression, we fail to reject the null hypothesis that population density have an direct impact to the COVID-19 case rate. There could be multiple factors causing the population density to be insignificant. For example, the population density is calculated by population divided by total square miles. As a result the numbers can be diluted for states that have major cities with high population density, but very little urbanization in the majority part of the state suburb area. In addition, as stated earlier in the research, Washington, D.C. is considered as a state however the demography structure and geographical related characteristics are different from other states. And due to a small sample we have, individual variables that exhibit unique characteristics could lead to certain degree of bias.

@@

CLM assumptions check for Model 3:

####Zero Conditional Mean

The Residual vs Fitted chat shows a almost flat line that is close to zero, with the tails a bit skewed. There is no strong evidence that there are unincoorperated linear relationship that we are not capturing from the control variables.
```{r}

plot(model3, which=1)
```

####Normality of errors
From the Normal Q-Q plot below, the points generally stay close to the normal line, with the tails exhibit certain degree of skew. 
```{r}
plot(model3, which=2)
```
####Homoskedasticity
```{r}

plot(model3, which=3)
```
```{r}
#Cook distance
plot(model3, which=5)
```
```{r}
#Collinearity
vif(model3)
```
